	\section{Input-Output}
	\mypackage{IO}

This package contains classes for input, output and plugin loading.

\myclass{PluginController}

\textbf{Beschreibung}

Loads all Heuristic, HeuristicResult and HeuristicProperties classes using the ServiceLoader class. It uses the singelton design pattern.

\textbf{Dokumentation}
\begin{enumerate}[+]
	\item{
		\textbf{getInstance():PluginController} \newline
		This method is the only way to access the PluginController. Creates a new PluginController if it does not exist. \newline
		\textbf{@return} returns the PluginController itself. \newline
	}
	\item{
		\textbf{getHeuristics():ArrayList<Heuristic> } \newline
		Loads all Heuristic classes if they are not already loaded. \newline
		\textbf{@return} returns a list with all Heuristics. \newline
	}
	\item{
		\textbf{getHeuristicResults():ArrayList<HeuristicResult>} \newline
		Loads all HeuristicResult classes if they are not already loaded. \newline
		\textbf{@return} returns a list with all HeuristicResult classes. \newline
	}
	\item{
		\textbf{getHeuristicProperties():ArrayList<HeuristicProperties>} \newline
		Loads all HeuristicProperties classes if they are not already loaded. \newline
		\textbf{@return} returns a list with all HeuristicProperties classes. \newline
	}
	\item{
		\textbf{reloadPlugins()} \newline
		Clears the pluginlists and then loads all plugins. \newline
	}
\end{enumerate}

\myclass{IOController}

\textbf{Beschreibung}

Saves and loads the data of a single view tab. The file has the extension \glqq.RAGE\grqq. It uses the singelton design pattern.

\textbf{Dokumentation}
\begin{enumerate}[+]
	\item{
		\textbf{getInstance():IOController} \newline
		This method is the only way to access the IOController. Creates a new IOController if it does not exist. \newline
		\textbf{@return} returns the IOController itself. \newline
	}
	\item{
		\textbf{writeFile(File file)} \newline
		Writes a RAGE file to the disk. \newline
		\textbf{@param file} Information about the file. \newline
		\textbf{@throws IOException} if saving fails print: \glqq Error while saving the file.\grqq.
	}
	\item{
		\textbf{readFile(File file)} \newline
		Reads a RAGE file from the disk and sends the content to the model. \newline
		\textbf{@param file} Information about the file. \newline
		\textbf{@throws IOException} if loading fails print: \glqq Error while loading the file.\grqq.
	}
\end{enumerate}